---
output: 
  html_document:
      css: styles.css
runtime: shiny
---

## Bay Segment Hydrologic Estimates & Adjustment Factors

```{r, warning = F, message = F, echo = F}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, echo = F)

library(knitr)
library(tidyverse)
library(kableExtra)

# # style file
# styles <- readLines('https://raw.githubusercontent.com/tbep-tech/css-styling/master/styles.css')
# writeLines(styles, 'styles.css')

data(yrests)
yrs <- unique(yrests$Year)
```

```{r reactive}
tabsel <- reactive({
   
   # input 
   yrsel <- input$yrsel
   
   totab <- yrests %>% 
      filter(Year == yrsel) %>% 
      select(-Year, -`Compliance Load`) 

   # tabular output
   out <- HTML(knitr::kable(totab, format = 'html', digits = 2) %>% 
      kable_styling(full_width = T, font_size = 14))
   
   return(out)
   
})
```

```{r}
column(12, 
       column(4, 
              selectInput('yrsel', 'Select year:', choices = yrs, selected = max(yrs))
       )
)
```

`r renderText(input$yrsel)` annual hydrologic adjustment factor results by bay segment, based upon regressions developed in [TBEP Technical Publication #03-16](https://drive.google.com/file/d/11NT0NQ2WbPO6pVZaD7P7Z6qjcwO1jxHw/view). Results are considered draft and may change with updates to USGS flow and rainfall data.  Consult the [annual compliance assessments reports](https://tbep.org/our-work/library/?table_filter=compliance){target="_blank"} for applicable load adjustment estimate
   
```{r, results = 'asis'}
renderUI(tabsel())
```